---
title: "First Visualization"
author: "Group6" 
output:
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
require(tidyr)
require(dplyr)
require(tibble)
require(lubridate)
require(ggplot2)
require(readr)


reviews <- read_csv("data/reviews.csv")
users <- read_csv("data/users.csv")
hotels <- read_csv("data/hotels.csv")
user_review <- reviews|>
  left_join(users, by = "user_id") |>
  select(user_id, user_gender, country, age_group, traveller_type, review_id, score_overall, score_cleanliness, score_comfort, score_facilities, score_location, score_staff, score_value_for_money)
```

# Q1. Which specific service component (e.g. staff, room service) has the greatest impact on the overall customer satisfaction?

## Cleanliness
```{r}
ggplot(reviews, aes(x = score_cleanliness, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score cleanliness",
       y = "score overall", 
       title = "Relationship Between Cleanliness and Overall Score")

cor(reviews$score_cleanliness, reviews$score_overall, method = "pearson")
```

## Comfort
```{r}
ggplot(reviews, aes(x = score_comfort, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score comfort",
       y = "score overall", 
       title = "Relationship Between Comfort and Overall Score")

cor(reviews$score_comfort, reviews$score_overall, method = "pearson")
```

## Facilities
```{r}
ggplot(reviews, aes(x = score_facilities, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score facilities",
       y = "score overall", 
       title = "Relationship Between Facilities and Overall Score")

cor(reviews$score_facilities, reviews$score_overall, method = "pearson")
```

## Location
```{r}
ggplot(reviews, aes(x = score_location, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score location",
       y = "score overall", 
       title = "Relationship Between Location and Overall Score")

cor(reviews$score_location, reviews$score_overall, method = "pearson")
```

## Staff
```{r}
ggplot(reviews, aes(x = score_staff, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score staff",
       y = "score overall", 
       title = "Relationship Between Staff and Overall Score")

cor(reviews$score_staff, reviews$score_overall, method = "pearson")
```

## Value for Money
```{r}
ggplot(reviews, aes(x = score_value_for_money, y = score_overall)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "score value for money",
       y = "score overall", 
       title = "Relationship Between Value for Money and Overall Score")

cor(reviews$score_value_for_money, reviews$score_overall, method = "pearson")
```

Conclusion: Cleanliness has the greatest impact on overall customer satisfaction among all service components examined. With a correlation coefficient of r = 0.544, cleanliness demonstrates a moderate to strong positive relationship with overall satisfaction scores.


# Q3. How does demographics (gender, age group of customers) influence review behavior?

## Gender
```{r data-preparation-boxplot,echo=FALSE, message=FALSE, warning=FALSE}
score_long <- user_review |>
  select(user_id,user_gender,age_group,traveller_type,starts_with("score_")) |>
  pivot_longer(
    cols = c(score_overall, score_cleanliness, score_comfort, score_facilities, 
             score_location, score_staff, score_value_for_money),          
    names_to = "Score_Type",               
    values_to = "Score_Value",
    names_prefix = "score_"
  ) |>
  mutate(
    Score_Type = case_when(
      Score_Type == "overall" ~ "Overall Score",
      Score_Type == "staff" ~ "Staff",
      Score_Type == "comfort" ~ "Comfort",
      Score_Type == "facilities" ~ "Facilities",
      Score_Type == "location" ~ "Location",
      Score_Type == "cleanliness" ~ "Cleanliness",
      Score_Type == "value_for_money" ~ "Value for Money",
      TRUE ~ Score_Type
    ),
    Score_Type = factor(Score_Type, levels = c(
      "Overall Score",      
      "Cleanliness",  
      "Comfort",
      "Facilities",
      "Location",
      "Staff",             
      "Value for Money"))
)
```

```{r gender-boxplot}
gender_boxplot_facet <- score_long |>
  ggplot(aes(x = user_gender, y = Score_Value)) +
  geom_boxplot(aes(fill = user_gender),
    alpha = 0.6,
    linewidth = 0.5) + 
    scale_fill_brewer(
    palette = "Set1"
  )+
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2.5, fill = "white", color = "black") +
  facet_grid(~Score_Type, scales = "fixed") +
  labs(
    title = "Score Distribution and Variance by Gender",
    x = "",
    y = "Score_value",
    fill = "Gender"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
gender_boxplot_facet
```
The boxplot analysis reveals a high similarity in median scores and variance on each service components (e.g., Cleanliness, Staff) for all gender groups.This suggests that gender is not a significant factor determining the absolute level of customer satisfaction or review behavior.

```{r data-preparation-scatter,echo=FALSE, message=FALSE, warning=FALSE}
scatter_data <- user_review |>
  select(user_id, user_gender, age_group, traveller_type, score_overall, 
         score_staff, score_comfort, score_facilities, 
         score_location, score_cleanliness, score_value_for_money) |>
  pivot_longer(
    cols = c(score_cleanliness, score_comfort, score_facilities, 
             score_location, score_staff, score_value_for_money), 
    names_to = "Service_Type",            
    values_to = "Service_Score",
    names_prefix = "score_"
  ) |>
  mutate(
    Service_Type = case_when(
      Service_Type == "cleanliness" ~ "Cleanliness",
      Service_Type == "comfort" ~ "Comfort",
      Service_Type == "facilities" ~ "Facilities",
      Service_Type == "location" ~ "Location",
      Service_Type == "staff" ~ "Staff",
      Service_Type == "value_for_money" ~ "Value for Money",
      TRUE ~ Service_Type
    )
  )

```

```{r gender-scatter}
gender_scatter_facet <- scatter_data |>
  ggplot(aes(x = Service_Score, y = score_overall, color = user_gender)) +
  geom_point(alpha = 0.1, size = 0.5) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.6) +
  facet_grid(~Service_Type, scales = "fixed") +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Linear Sensitivity of Scores by Gender",
    x = "Service Score",
    y = "Score Overall",
    color = "Gender"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
gender_scatter_facet
```
The scatter plot reveals that gender does not influence service priority or the overall score.


## Age Group(18-24, 25-34, 35-44, 45-54, 55+)
```{r age-boxplot}
age_boxplot_facet <- score_long |>
  ggplot(aes(x = age_group, y = Score_Value)) +
  geom_boxplot(aes(fill = age_group),
    alpha = 0.6,
    linewidth = 0.5) + 
  scale_fill_brewer(
    palette = "Set1"
  )+
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2.5, fill = "white", color = "black") +
  facet_grid(~Score_Type, scales = "fixed") +
  labs(
    title = "Score Distribution and Variance by Age Group",
    x = "",
    y = "Score_value",
    fill = "Age Group"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
age_boxplot_facet
```
The boxplot analysis reveals a high similarity in median scores and variance on each service component (e.g., Cleanliness, Staff) for all age groups.This suggests that age is not a significant factor determining the absolute level of customer satisfaction or review behavior.

```{r age-scatter}
age_scatter_facet <- scatter_data |>
  ggplot(aes(x = Service_Score, y = score_overall, color = age_group)) +
  geom_point(alpha = 0.1, size = 0.5) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.6) +
  facet_grid(~Service_Type, scales = "fixed") +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Linear Sensitivity of Scores by Age Group",
    x = "Service Score",
    y = "Score Overall",
    color = "Age Group"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
age_scatter_facet
```
The scatter plot reveals that age does not influence service priority or the overall score.

# Q4. How do traveler types (Family, Couple, Business) influence review behavior?

## Traveller Type(Business, Couple, Family, Solo)
```{r traveller-type-boxplot}
type_boxplot_facet <- score_long |>
  ggplot(aes(x = traveller_type, y = Score_Value)) +
  geom_boxplot(aes(fill = traveller_type),
    alpha = 0.6,
    linewidth = 0.5) + 
  scale_fill_brewer(
    palette = "Set1"
  )+
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2.5, fill = "white", color = "black") +
  facet_grid(~Score_Type, scales = "fixed") +
  labs(
    title = "Score Distribution and Variance by Traveller Type",
    x = "",
    y = "Score_value",
    fill = "Traveller Type"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
type_boxplot_facet
```

Based on the visualization, several insights can be drawn about traveller type differences in hotel satisfaction:

Business travellers give notably low scores for "Value for Money", which might suggest that they feel they are overpaying for what they receive. In contrast, "Location" receives the highest score from this group, likely due to the importance of accessibility to business districts and transport for work-related trips.

Couple travellers provide higher median scores for "Cleanliness" and "Comfort" compared to other groups, which indicating that these two are key factors in their satisfaction.

Families are generally well-satisfied, scoring cleanliness and facilities the highest.They also maintain solid scores for "Staff" and "Value for Money".

Solo travellers rate "Staff" and "Value for Money" relatively high, suggesting that friendly service and cost-effectiveness play crucial roles in their decision-making.


```{r traveller-type-scatter}
type_scatter_facet <- scatter_data |>
  ggplot(aes(x = Service_Score, y = score_overall, color = traveller_type)) +
  geom_point(alpha = 0.1, size = 0.5) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.6) +
  facet_grid(~Service_Type, scales = "fixed") +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Linear Sensitivity of Scores by Traveller Type",
    x = "Service Score",
    y = "Score Overall",
    color = "Traveller Type"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"), 
    axis.text.x = element_blank(),                       
    axis.ticks.x = element_blank(),                      
    panel.grid.major.x = element_blank(),                
    legend.position = "bottom"                           
  )
type_scatter_facet
```

The chart shows that sensitivity to service items is generally similar across all traveller types (Business, Couple, Family, Solo). This similarity in slope means that the importance (weight) of most service scores on the overall rating is distributed similarly among all guests.

However, a relatively clear difference is visible for Value for Money: The red line (Business) is notably flatter, while the purple line (Solo), along with the green (Family) and blue (Couple) lines, are all steeper. This suggests that solo travellers (and family and couple travellers) are more sensitive to changes in the Value for Money score, and thus place a higher weight on it when forming their final overall rating, compared to Business travellers.
