---
title: "PBA Final Report - Data processing & analysis"
author: "Group6 - Yichi Tseng (114078513), Ting-Wen Liu (114078518)"
output:
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
require(tidyverse)
require(infer)
require(tibble)
require(ggplot2)
require(readr)
require(lmerTest)
require(performance)
library(broom.mixed)
library(knitr)
```

# Data processing 
1. Read the data
```{r}
exp_data <- read_csv(url("https://drive.google.com/uc?export=download&id=1estf46syRbfG2K8JfW9myfTq2qDp0Ums"))
```
2. Select and rename the columns
```{r}
df <- exp_data |>
  select('id', 'treatment', 'hotel1', 'hotel2', 'hotel3') |>
  pivot_longer(
    cols = c('hotel1', 'hotel2', 'hotel3'),
    names_to = 'hotel',
    values_to = 'score'
  ) |>
  mutate(
    scenario =  case_when(
      hotel == "hotel1" ~ "negative",
      hotel == "hotel2" ~ "neutral",
      hotel == "hotel3" ~ "positive"
    )
  )
df
```
3. Check the data completeness
```{r}
table(df$id)
```
# EDA
1. Boxplot
```{r}
ggplot(df, aes(x = scenario, y = score)) +
  geom_boxplot() +
  labs(title = "Hotel Ratings by Scenario")
```

2. Boxplot with treatment
```{r}
ggplot(df, aes(x = scenario, y = score, fill = factor(treatment))) +
  geom_boxplot(position = position_dodge()) +
  labs(title = "Hotel Ratings by Scenario", fill = "Treatment") 
```

# Linear Mixed Model Analysis
1. Set the 'neutral' scene as the baseline.
```{r}
df$treatment <- factor(df$treatment)
df$scenario  <- factor(df$scenario,
                        levels = c("neutral", "positive", "negative"))
```

2. Model
```{r}
m1 <- lmer(
  score ~ treatment * scenario + (1 | id),
  data = df
)
```

3. Statistic summary
```{r}
summary(m1)
```

4. Fixed effect
```{r}
tidy_m1 <- tidy(m1, effects = "fixed")
kable(tidy_m1, digits = 3)
```

5. Check the Model fit
```{r}
r2 <- r2(m1)
kable(r2, digits = 3)
```

# Bootstrap resampling for the neutral hotel scenario
1. Bootstrap
```{r}
df_neutral <- df %>% filter(scenario == "neutral")
ate_boots <- df_neutral |>
  rep_slice_sample(prop = 1, reps = 1000, replace = TRUE) |>
  group_by(replicate, treatment) |>
  summarize(mean_score = mean(score, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(
    names_from = treatment,
    values_from = mean_score
  ) |>
  mutate(ate = `1` - `0`);ate_boots
```

2. Calculate the 95% confidence interval
```{r} 
boot_ci <- quantile(ate_boots$ate, c(0.025, 0.975))

boot_ci
```

3. Visualize the ate distribution
```{r}
ggplot(ate_boots, aes(x=ate)) +
    geom_histogram(aes(y = after_stat(density)), color = "white") +
    geom_vline(xintercept = unlist(boot_ci), linewidth = 1)
```
